---
title: "Supplementary figures"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=12, fig.height=20, message=FALSE, warning =FALSE)
```

```{r, include=FALSE}
rm(list=ls())
library(tidyverse)
library(knitr)
library(here)
load("C:/Users/andre/Dropbox/WASHB-EE-analysis/WBB-EE-analysis/Results/Andrew/FU2_results.RDATA")
load("C:/Users/andre/Dropbox/WASHB-EE-analysis/WBB-EE-analysis/Results/Andrew/FU2_pooled_results.Rdata")

#Plot parameters
scaleFUN <- function(x) sprintf("%.2f", x)

#Plot themes
theme_set(theme_bw())

#hbgdki pallet
tableau10 <- c("#1F77B4","#FF7F0E","#2CA02C","#D62728",
  "#9467BD","#8C564B","#E377C2","#7F7F7F","#BCBD22","#17BECF")

  
```


<!-- ## Supplementary Figure 1: Child FUT2 status effect on continuous growth outcomes -->

<!-- ```{r, echo=F, fig.width=12, fig.height=8} -->
<!-- plotdf <-data.frame(X= rownames(pooled_childFU2_growthRF_cont), pooled_childFU2_growthRF_cont) -->
<!-- plotdf$outcome <- substr(plotdf$X, 1,3) -->
<!-- plotdf$X <- factor(plotdf$X, levels=c("LAZ", "WHZ", "WAZ", "HCZ")) -->
<!-- plotdf <- plotdf %>% arrange(X) -->
<!-- ggplot(plotdf, aes(x=X)) +  -->
<!--         geom_point(aes(y=ATE, fill=X, color=X), size = 4) + -->
<!--         geom_linerange(aes(ymin=ci.l, ymax=ci.u, color=X), -->
<!--                        alpha=0.5, size = 3) + -->
<!--         labs(x = "Continuous growth outcome", y = "Difference in Z-scores") + -->
<!--         geom_hline(yintercept = 0) + -->
<!--         scale_fill_manual(values=rep(tableau10,4)) + -->
<!--         scale_colour_manual(values=rep(tableau10,4)) + -->
<!--         theme(strip.background = element_blank(), -->
<!--           legend.position="none", -->
<!--           strip.text.x = element_text(size=12), -->
<!--           axis.text.x = element_text(size=12, angle = 60, hjust = 1)) + -->
<!--         ggtitle("FUT2 Negative (non-secretor) minus FUT2 Positive (secretor)") -->
<!-- ``` -->

<!-- ## Supplementary Figure 2: Child FUT2 status effect on binary growth outcomes -->


<!-- ```{r, echo=F, fig.width=12, fig.height=8} -->
<!-- plotdf <- data.frame(X= rownames(pooled_childFU2_growthRF_bin), pooled_childFU2_growthRF_bin) -->
<!-- plotdf$RR[plotdf$X=="Severe wasted - 3 months"] <- NA #Temp drop extreme estimates -->
<!-- plotdf$ci.l[plotdf$X=="Severe wasted - 3 months"] <- NA -->
<!-- plotdf$ci.u[plotdf$X=="Severe wasted - 3 months"] <- NA -->

<!-- plotdf$X <- factor(plotdf$X, levels=c("Stunted", "Wasted", "Underweight", "Severe stunted", "Severe wasted", "Severe underweight")) -->

<!-- plotdf$outcome <- substr(plotdf$X, 1,9) -->
<!-- ggplot(plotdf, aes(x=X)) +  -->
<!--         geom_point(aes(y=RR, fill=X, color=X), size = 4) + -->
<!--         geom_linerange(aes(ymin=ci.l, ymax=ci.u, color=X), -->
<!--                        alpha=0.5, size = 3) + -->
<!--         labs(x = "Binary growth outcome", y = "Prevalence ratio") + -->
<!--   scale_y_continuous(trans='log10') + -->
<!--         geom_hline(yintercept = 1) + -->
<!--         scale_fill_manual(values=rep(tableau10,4)) + -->
<!--         scale_colour_manual(values=rep(tableau10,4)) + -->
<!--         theme(strip.background = element_blank(), -->
<!--           legend.position="none", -->
<!--           strip.text.x = element_text(size=12), -->
<!--           axis.text.x = element_text(size=12, angle = 60, hjust = 1)) + -->
<!--         ggtitle("Ratio of FUT2 Negative (non-secretor) over FUT2 Positive (secretor)") -->
<!-- ``` -->

<!-- ## Supplementary Figure 3: Mother FUT2 status effect on continuous growth outcomes -->

<!-- ```{r, echo=F, fig.width=12, fig.height=8} -->
<!-- plotdf <-data.frame(X= rownames(pooled_motherFU2_growthRF_cont), pooled_motherFU2_growthRF_cont) -->
<!-- plotdf$outcome <- sapply(strsplit(as.character(plotdf$X), " -", fixed=T), `[`, 1) -->

<!-- plotdf$X <- factor(plotdf$X, levels=c("LAZ", "WHZ", "WAZ", "HCZ")) -->
<!-- plotdf <- plotdf %>% arrange(X) -->

<!-- ggplot(plotdf, aes(x=X)) +  -->
<!--         geom_point(aes(y=ATE, fill=X, color=X), size = 4) + -->
<!--         geom_linerange(aes(ymin=ci.l, ymax=ci.u, color=X), -->
<!--                        alpha=0.5, size = 3) + -->
<!--         labs(x = "Continuous growth outcome", y = "Difference in Z-scores") + -->
<!--         geom_hline(yintercept = 0) + -->
<!--         scale_fill_manual(values=rep(tableau10,4)) + -->
<!--         scale_colour_manual(values=rep(tableau10,4)) + -->
<!--         theme(strip.background = element_blank(), -->
<!--           legend.position="none", -->
<!--           strip.text.x = element_text(size=12), -->
<!--           axis.text.x = element_text(size=12, angle = 60, hjust = 1)) + -->
<!--         ggtitle("FUT2 Negative (non-secretor) minus FUT2 Positive (secretor)") -->
<!-- ``` -->

<!-- ## Supplementary Figure 4: Mother FUT2 status effect on binary growth outcomes -->

<!-- ```{r, echo=F, fig.width=12, fig.height=8} -->
<!-- plotdf <-data.frame(X= rownames(pooled_motherFU2_growthRF_bin), pooled_motherFU2_growthRF_bin) -->
<!-- plotdf$RR[plotdf$X=="Severe wasted - 3 months"] <- NA #Temp drop extreme estimates -->
<!-- plotdf$ci.l[plotdf$X=="Severe wasted - 3 months"] <- NA -->
<!-- plotdf$ci.u[plotdf$X=="Severe wasted - 3 months"] <- NA -->

<!-- plotdf$X <- factor(plotdf$X, levels=c("Stunted", "Wasted", "Underweight", "Severe stunted", "Severe wasted", "Severe underweight")) -->


<!-- plotdf$outcome <- sapply(strsplit(as.character(plotdf$X), " -", fixed=T), `[`, 1) -->

<!-- ggplot(plotdf, aes(x=X)) +  -->
<!--         geom_point(aes(y=RR, fill=outcome, color=outcome), size = 4) + -->
<!--         geom_linerange(aes(ymin=ci.l, ymax=ci.u, color=outcome), -->
<!--                        alpha=0.5, size = 3) + -->
<!--         labs(x = "Binary growth outcome", y = "Prevalence ratio") + -->
<!--   scale_y_continuous(trans='log10') + -->
<!--         geom_hline(yintercept = 1) +        scale_fill_manual(values=rep(tableau10,4)) + -->
<!--         scale_colour_manual(values=rep(tableau10,4)) + -->
<!--         theme(strip.background = element_blank(), -->
<!--           legend.position="none", -->
<!--           strip.text.x = element_text(size=12), -->
<!--           axis.text.x = element_text(size=12, angle = 60, hjust = 1)) + -->
<!--         ggtitle("Ratio of FUT2 Negative (non-secretor) over FUT2 Positive (secretor)") -->
<!-- ``` -->


<!-- ## Supplementary Figure 5: Child FUT2 status effect on EED outcomes -->


<!-- ```{r, echo=F, fig.width=12, fig.height=8} -->
<!-- plotdf <-data.frame(X= rownames(pooled_childFU2_RF_adj), pooled_childFU2_RF_adj) -->



<!-- plotdf$X <- factor(plotdf$X, levels=c("Lactulose", "Mannitol", "L/M ratio", "Alpha-1 antitrypsin", "Myeloperoxidase", "Neopterin", "Regenerating gene 1B")) -->



<!-- plotdf$outcome <- substr(plotdf$X, 1,2) -->
<!-- ggplot(plotdf, aes(x=X)) +  -->
<!--         geom_point(aes(y=ATE, fill=X, color=X), size = 4) + -->
<!--         geom_linerange(aes(ymin=ci.l, ymax=ci.u, color=X), -->
<!--                        alpha=0.5, size = 3) + -->
<!--         labs(x = "EED outcome", y = "Difference in log-transformed outcomes") + -->
<!--         geom_hline(yintercept = 0) + -->
<!--         scale_fill_manual(values=rep(tableau10,4)) + -->
<!--         scale_colour_manual(values=rep(tableau10,4)) + -->
<!--         theme(strip.background = element_blank(), -->
<!--           legend.position="none", -->
<!--           strip.text.x = element_text(size=12), -->
<!--           axis.text.x = element_text(size=12, angle = 60, hjust = 1)) + -->
<!--         ggtitle("FUT2 Negative (non-secretor) minus FUT2 Positive (secretor)") -->
<!-- ``` -->

<!-- ## Supplementary Figure 6: Mother's FUT2 status effect on EED outcomes -->

<!-- ```{r, echo=F, fig.width=12, fig.height=8} -->
<!-- plotdf <-data.frame(X= rownames(pooled_motherFU2_RF_adj), pooled_motherFU2_RF_adj) -->
<!-- plotdf$outcome <- substr(plotdf$X, 1,2) -->

<!-- plotdf$X <- factor(plotdf$X, levels=c("Lactulose", "Mannitol", "L/M ratio", "Alpha-1 antitrypsin", "Myeloperoxidase", "Neopterin", "Regenerating gene 1B")) -->

<!-- ggplot(plotdf, aes(x=X)) +  -->
<!--         geom_point(aes(y=ATE, fill=X, color=X), size = 4) + -->
<!--         geom_linerange(aes(ymin=ci.l, ymax=ci.u, color=X), -->
<!--                        alpha=0.5, size = 3) + -->
<!--         labs(x = "EED outcome", y = "Difference in log-transformed outcomes") + -->
<!--         geom_hline(yintercept = 0) + -->
<!--         scale_fill_manual(values=rep(tableau10,4)) + -->
<!--         scale_colour_manual(values=rep(tableau10,4)) + -->
<!--         theme(strip.background = element_blank(), -->
<!--           legend.position="none", -->
<!--           strip.text.x = element_text(size=12), -->
<!--           axis.text.x = element_text(size=12, angle = 60, hjust = 1)) + -->
<!--         ggtitle("FUT2 Negative (non-secretor) minus FUT2 Positive (secretor)") -->
<!-- ``` -->




## Supplementary Figure 1: WASH Benefits intervention effects, stratified by child FUT2 status (FUT2 as an effect modifier)

Note: stars above the plotted points indicate that the P-value of the interaction term between treatment and FUT2 status is < 0.05.

Columns are sampling round, and rows are EED outcomes.


```{r, echo=F}

C_plot_EM<- ggplot(resC, aes(x=X)) + 
        geom_point(aes(y=`Unadj. diff.`, fill=Contrast, color=Contrast), size = 4) +
        geom_linerange(aes(ymin=ci.l, ymax=ci.u, color=Contrast),
                       alpha=0.5, size = 3) +
        labs(x = "Treatment contrast and FUT2 status", y = "Average treatment effect") +
        geom_text(aes(x=X, y=ci.u+0.02, label=ifelse(resC$InteractionPval<0.05,"*",""))) + 
        geom_hline(yintercept = 0) +
        #coord_cartesian(ylim=range(yticks)) +
        scale_fill_manual(values=rep(tableau10,4)) +
        scale_colour_manual(values=rep(tableau10,4)) +
        scale_size_continuous(range = c(0.5, 1))+
        theme(strip.background = element_blank(),
          legend.position="none",
          strip.text.x = element_text(size=12),
          axis.text.x = element_text(size=12, angle = 45, hjust = 1), 
          strip.text.y = element_text(angle = 0)) +
        facet_grid(biomarker~Round,) +
        ggtitle("Child FUT2 status")


M_plot_EM<- ggplot(resM, aes(x=X)) + 
        geom_point(aes(y=`Unadj. diff.`, fill=Contrast, color=Contrast), size = 4) +
        geom_linerange(aes(ymin=ci.l, ymax=ci.u, color=Contrast),
                       alpha=0.5, size = 3) +
        labs(x = "Treatment contrast and FUT2 status", y = "Average treatment effect") +
        geom_text(aes(x=X, y=ci.u+0.02, label=ifelse(resM$InteractionPval<0.05,"*",""))) + 
        geom_hline(yintercept = 0) +
        #coord_cartesian(ylim=range(yticks)) +
        scale_fill_manual(values=rep(tableau10,4)) +
        scale_colour_manual(values=rep(tableau10,4)) +
        scale_size_continuous(range = c(0.5, 1))+
        theme(strip.background = element_blank(),
          legend.position="none",
          strip.text.x = element_text(size=12),
          axis.text.x = element_text(size=12, angle = 45, hjust = 1), 
          strip.text.y = element_text(angle = 0)) +
          facet_grid(biomarker~Round) +
        ggtitle("Mother FUT2 status")

print(C_plot_EM)
```

## Supplementary Figure 2: WASH Benefits intervention effects, stratified by maternal FUT2 status (FUT2 as an effect modifier)

Note: stars above the plotted points indicate that the P-value of the interaction term between treatment and FUT2 status is < 0.05.

Columns are sampling round, and rows are EED outcomes.


```{r, echo=F}
print(M_plot_EM)
```


## Supplementary Figure 3: Child FUT2 status effect on continuous growth outcomes, stratified by measurement round

```{r, echo=F, fig.width=12, fig.height=8}
plotdf <-data.frame(X= rownames(res_childFU2_growthRF_cont), res_childFU2_growthRF_cont)

  plotdf$X <- gsub("T1", "3 months", plotdf$X)
  plotdf$X <- gsub("T2", "1 year", plotdf$X)
  plotdf$X <- gsub("T3", "2 years", plotdf$X)

plotdf$X <- factor(plotdf$X, levels=c("LAZ - 3 months", "LAZ - 1 year", "LAZ - 2 years", 
									  "WHZ - 3 months", "WHZ - 1 year", "WHZ - 2 years",
									  "WAZ - 3 months", "WAZ - 1 year", "WAZ - 2 years",
									  "HCZ - 3 months", "HCZ - 1 year", "HCZ - 2 years"))
plotdf <- plotdf %>% arrange(X)

plotdf$outcome <- substr(plotdf$X, 1,2)
plotdf$outcome <- factor(plotdf$outcome, levels=unique(plotdf$outcome))

ggplot(plotdf, aes(x=X)) + 
        geom_point(aes(y=ATE, fill=outcome, color=outcome), size = 4) +
        geom_linerange(aes(ymin=ci.l, ymax=ci.u, color=outcome),
                       alpha=0.5, size = 3) +
        labs(x = "Continuous growth outcome", y = "Difference in Z-scores") +
        geom_hline(yintercept = 0) +
        scale_fill_manual(values=rep(tableau10,4)) +
        scale_colour_manual(values=rep(tableau10,4)) +
        theme(strip.background = element_blank(),
          legend.position="none",
          strip.text.x = element_text(size=12),
          axis.text.x = element_text(size=12, angle = 60, hjust = 1)) +
        ggtitle("FUT2 Negative (non-secretor) minus FUT2 Positive (secretor)")
```

## Supplementary Figure 4: Child FUT2 status effect on binary growth outcomes, stratified by measurement round

Note that severe wasting is very rare, with only 16 cases at time one and three, and 19 at time two. There are 0 cases of severe wasting among non-secretor at time 1, leading to an unstable, very small prevalence ratio estimate (2.32 x 10^-08). This estimate has been excluded from the below figure. 

```{r, echo=F, fig.width=12, fig.height=8}
plotdf <- data.frame(X= rownames(res_childFU2_growthRF_bin), res_childFU2_growthRF_bin)

  plotdf$X <- gsub("T1", "3 months", plotdf$X)
  plotdf$X <- gsub("T2", "1 year", plotdf$X)
  plotdf$X <- gsub("T3", "2 years", plotdf$X)
  
plotdf$RR[plotdf$X=="Severe wasted - 3 months"] <- NA #Temp drop extreme estimates
plotdf$ci.l[plotdf$X=="Severe wasted - 3 months"] <- NA
plotdf$ci.u[plotdf$X=="Severe wasted - 3 months"] <- NA



plotdf$X <- factor(plotdf$X, levels=c("Stunted - 3 months", "Stunted - 1 year", "Stunted - 2 years", 
									  "Wasted - 3 months", "Wasted - 1 year", "Wasted - 2 years",
									  "Underweight - 3 months", "Underweight - 1 year", "Underweight - 2 years",
									  "Severe stunted - 3 months", "Severe stunted - 1 year", "Severe stunted - 2 years", 
									  "Severe wasted - 3 months", "Severe wasted - 1 year", "Severe wasted - 2 years",
									  "Severe underweight - 3 months", "Severe underweight - 1 year", "Severe underweight - 2 years"))
plotdf <- plotdf %>% arrange(X)

plotdf$outcome <- substr(plotdf$X, 1,9)
plotdf$outcome <- factor(plotdf$outcome, levels=unique(plotdf$outcome))


ggplot(plotdf, aes(x=X)) + 
        geom_point(aes(y=RR, fill=outcome, color=outcome), size = 4) +
        geom_linerange(aes(ymin=ci.l, ymax=ci.u, color=outcome),
                       alpha=0.5, size = 3) +
        labs(x = "Binary growth outcome", y = "Prevalence ratio") +
  scale_y_continuous(trans='log10') +
        geom_hline(yintercept = 1) +
        scale_fill_manual(values=rep(tableau10,4)) +
        scale_colour_manual(values=rep(tableau10,4)) +
        theme(strip.background = element_blank(),
          legend.position="none",
          strip.text.x = element_text(size=12),
          axis.text.x = element_text(size=12, angle = 60, hjust = 1)) +
        ggtitle("Ratio of FUT2 Negative (non-secretor) over FUT2 Positive (secretor)")
```

## Supplementary Figure 5: Maternal FUT2 status effect on continious growth outcomes, stratified by measurement round

```{r, echo=F, fig.width=12, fig.height=8}
plotdf <-data.frame(X= rownames(res_motherFU2_growthRF_cont), res_motherFU2_growthRF_cont)

  plotdf$X <- gsub("T1", "3 months", plotdf$X)
  plotdf$X <- gsub("T2", "1 year", plotdf$X)
  plotdf$X <- gsub("T3", "2 years", plotdf$X)
  
plotdf$outcome <- sapply(strsplit(as.character(plotdf$X), " -", fixed=T), `[`, 1)

plotdf$X <- factor(plotdf$X, levels=c("LAZ - 3 months", "LAZ - 1 year", "LAZ - 2 years", 
									  "WHZ - 3 months", "WHZ - 1 year", "WHZ - 2 years",
									  "WAZ - 3 months", "WAZ - 1 year", "WAZ - 2 years",
									  "HCZ - 3 months", "HCZ - 1 year", "HCZ - 2 years"))
plotdf <- plotdf %>% arrange(X)

plotdf$outcome <- substr(plotdf$X, 1,2)
plotdf$outcome <- factor(plotdf$outcome, levels=unique(plotdf$outcome))

ggplot(plotdf, aes(x=X)) + 
        geom_point(aes(y=ATE, fill=outcome, color=outcome), size = 4) +
        geom_linerange(aes(ymin=ci.l, ymax=ci.u, color=outcome),
                       alpha=0.5, size = 3) +
        labs(x = "Continuous growth outcome", y = "Difference in Z-scores") +
        geom_hline(yintercept = 0) +
        scale_fill_manual(values=rep(tableau10,4)) +
        scale_colour_manual(values=rep(tableau10,4)) +
        theme(strip.background = element_blank(),
          legend.position="none",
          strip.text.x = element_text(size=12),
          axis.text.x = element_text(size=12, angle = 60, hjust = 1)) +
        ggtitle("FUT2 Negative (non-secretor) minus FUT2 Positive (secretor)")
```

## Supplementary Figure 6: Maternal FUT2 status effect on binary growth outcomes, stratified by measurement round

```{r, echo=F, fig.width=12, fig.height=8}
plotdf <-data.frame(X= rownames(res_motherFU2_growthRF_bin), res_motherFU2_growthRF_bin)

  plotdf$X <- gsub("T1", "3 months", plotdf$X)
  plotdf$X <- gsub("T2", "1 year", plotdf$X)
  plotdf$X <- gsub("T3", "2 years", plotdf$X)
  
plotdf$RR[plotdf$X=="Severe wasted - 3 months"] <- NA #Temp drop extreme estimates
plotdf$ci.l[plotdf$X=="Severe wasted - 3 months"] <- NA
plotdf$ci.u[plotdf$X=="Severe wasted - 3 months"] <- NA

plotdf$X <- factor(plotdf$X, levels=c("Stunted - 3 months", "Stunted - 1 year", "Stunted - 2 years", 
									  "Wasted - 3 months", "Wasted - 1 year", "Wasted - 2 years",
									  "Underweight - 3 months", "Underweight - 1 year", "Underweight - 2 years",
									  "Severe stunted - 3 months", "Severe stunted - 1 year", "Severe stunted - 2 years", 
									  "Severe wasted - 3 months", "Severe wasted - 1 year", "Severe wasted - 2 years",
									  "Severe underweight - 3 months", "Severe underweight - 1 year", "Severe underweight - 2 years"))
plotdf <- plotdf %>% arrange(X)

plotdf$outcome <- sapply(strsplit(as.character(plotdf$X), " -", fixed=T), `[`, 1)
plotdf$outcome <- factor(plotdf$outcome, levels=unique(plotdf$outcome))


ggplot(plotdf, aes(x=X)) + 
        geom_point(aes(y=RR, fill=outcome, color=outcome), size = 4) +
        geom_linerange(aes(ymin=ci.l, ymax=ci.u, color=outcome),
                       alpha=0.5, size = 3) +
        labs(x = "Binary growth outcome", y = "Prevalence ratio") +
  scale_y_continuous(trans='log10') +
        geom_hline(yintercept = 1) +        scale_fill_manual(values=rep(tableau10,4)) +
        scale_colour_manual(values=rep(tableau10,4)) +
        theme(strip.background = element_blank(),
          legend.position="none",
          strip.text.x = element_text(size=12),
          axis.text.x = element_text(size=12, angle = 60, hjust = 1)) +
        ggtitle("Ratio of FUT2 Negative (non-secretor) over FUT2 Positive (secretor)")
```


## Supplementary Figure 7: Child FUT2 status effect on EED outcomes, stratified by measurement round


```{r, echo=F, fig.width=12, fig.height=8}
plotdf <-data.frame(X= rownames(res_childFU2_RF_adj), res_childFU2_RF_adj)


  plotdf$X <- gsub("T1", "3 months", plotdf$X)
  plotdf$X <- gsub("T2", "1 year", plotdf$X)
  plotdf$X <- gsub("T3", "2 years", plotdf$X)
  
plotdf$X <- factor(plotdf$X, levels=c("Lactulose - 3 months", "Lactulose - 1 year", "Lactulose - 2 years", 
									  "Mannitol - 3 months", "Mannitol - 1 year", "Mannitol - 2 years",
									  "L/M ratio - 3 months", "L/M ratio - 1 year", "L/M ratio - 2 years",
									  "Alpha-1 antitrypsin - 3 months", "Alpha-1 antitrypsin - 1 year", "Alpha-1 antitrypsin - 2 years",					
									  "Neopterin - 3 months", "Neopterin - 1 year", "Neopterin - 2 years",
									  "Myeloperoxidase - 3 months", "Myeloperoxidase - 1 year", "Myeloperoxidase - 2 years",
									  "Regenerating gene 1B - 1 year" ))
plotdf <- plotdf %>% arrange(X)

plotdf$outcome <- substr(plotdf$X, 1,2)
plotdf$outcome <- factor(plotdf$outcome, levels=unique(plotdf$outcome))
ggplot(plotdf, aes(x=X)) + 
        geom_point(aes(y=ATE, fill=outcome, color=outcome), size = 4) +
        geom_linerange(aes(ymin=ci.l, ymax=ci.u, color=outcome),
                       alpha=0.5, size = 3) +
        labs(x = "EED outcome", y = "Difference in log-transformed outcomes") +
        geom_hline(yintercept = 0) +
        scale_fill_manual(values=rep(tableau10,4)) +
        scale_colour_manual(values=rep(tableau10,4)) +
        theme(strip.background = element_blank(),
          legend.position="none",
          strip.text.x = element_text(size=12),
          axis.text.x = element_text(size=12, angle = 60, hjust = 1)) +
        ggtitle("FUT2 Negative (non-secretor) minus FUT2 Positive (secretor)")
```

## Supplementary Figure 8: Maternal FUT2 status effect on EED outcomes, stratified by measurement round

```{r, echo=F, fig.width=12, fig.height=8}
plotdf <-data.frame(X= rownames(res_motherFU2_RF_adj), res_motherFU2_RF_adj)

  plotdf$X <- gsub("T1", "3 months", plotdf$X)
  plotdf$X <- gsub("T2", "1 year", plotdf$X)
  plotdf$X <- gsub("T3", "2 years", plotdf$X)
  
plotdf$X <- factor(plotdf$X, levels=c("Lactulose - 3 months", "Lactulose - 1 year", "Lactulose - 2 years", 
									  "Mannitol - 3 months", "Mannitol - 1 year", "Mannitol - 2 years",
									  "L/M ratio - 3 months", "L/M ratio - 1 year", "L/M ratio - 2 years",
									  "Alpha-1 antitrypsin - 3 months", "Alpha-1 antitrypsin - 1 year", "Alpha-1 antitrypsin - 2 years",					
									  "Neopterin - 3 months", "Neopterin - 1 year", "Neopterin - 2 years",
									  "Myeloperoxidase - 3 months", "Myeloperoxidase - 1 year", "Myeloperoxidase - 2 years",
									  "Regenerating gene 1B - 1 year" ))
plotdf <- plotdf %>% arrange(X)

plotdf$outcome <- substr(plotdf$X, 1,2)
plotdf$outcome <- factor(plotdf$outcome, levels=unique(plotdf$outcome))

ggplot(plotdf, aes(x=X)) + 
        geom_point(aes(y=ATE, fill=outcome, color=outcome), size = 4) +
        geom_linerange(aes(ymin=ci.l, ymax=ci.u, color=outcome),
                       alpha=0.5, size = 3) +
        labs(x = "EED outcome", y = "Difference in log-transformed outcomes") +
        geom_hline(yintercept = 0) +
        scale_fill_manual(values=rep(tableau10,4)) +
        scale_colour_manual(values=rep(tableau10,4)) +
        theme(strip.background = element_blank(),
          legend.position="none",
          strip.text.x = element_text(size=12),
          axis.text.x = element_text(size=12, angle = 60, hjust = 1)) +
        ggtitle("FUT2 Negative (non-secretor) minus FUT2 Positive (secretor)")
```

